---
title: "blblm-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{blblm-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Introduction
  In this final project, we are going to work on bag of little bootstraps algorithm. This package has a implemented the bag of little bootstraps for linear regression model. My goal is to improve this package to various ways. 

  First of all, in the current implementation there is only one CPU is used in the algorithm. I used `future_map` in the `furrr` library and made it possible to use more than one CPUs. The users can decide if they want to use parallelization by specifying `n_cl`.
  Next, I added some descriptions for the functions. I also added test for `blblm`.

```{r setup}
library(blblm)
```

```{r}
blblm <- function(formula, data, m = 10, B = 5000, n_cl = 1) {
  data_list <- split_data(data, m)
  if(n_cl == 1){
    estimates <- map(
      data_list,
      ~ lm_each_subsample(formula = formula, data = ., n = nrow(data), B = B))
  } else {
    plan(multiprocess, workers = n_cl)
    estimates <- future_map(
      data_list,
      ~ lm_each_subsample(formula = formula, data = ., n = nrow(data), B = B))
  }
  res <- list(estimates = estimates, formula = formula)
  class(res) <- "blblm"
  invisible(res)
}
```

Here I wrote improved the original `blblm` to make it capabel with parallelization. 
`formula` is the formula we want to specify the linear regression
`data` is the dataset we are using to perform blblm
`m` is the number of subsamples(observations) to split the data
`B` is the number of bootstraps
`n_cl` is the number of clusters(cores) we use, if `n_cl` is greater than 1, then parallelization is used.


